---
title       : Pitch
subtitle    : Data Products Project
author      : Zach Fetterman
job         : Student
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## The Problem
<br />

* People all over the world use many different currencies in their daily lives.
* It can often be confusing to convert from one to the other.
* Incorrectly converting from one currency to the other can lead to serious headaches.

```{r}
16.25 * 1.14 # = ??? 
```

---

## The Solution
<br />

Our Data Product will ensure that you never again have trouble converting currencies from around the world.

Features

* Easy to use input
* Reactive design
* Useful exchange rate graph

---

## Example

```{r echo=FALSE}
library(ggplot2)

months <- seq(1, 23, by=1)
rate <- c(1.3167, 1.2999, 1.3010, 1.3302, 1.3222, 1.3526, 1.3584, 1.3591, 1.3746, 1.3487, 1.3802, 1.3771, 1.3867, 1.3631, 1.3692, 1.3389, 1.3133, 1.2632, 1.2525, 1.2452, 1.2099, 1.1288, 1.1383)
    
qplot(months, rate, geom="line", main="USD vs EUR", xlab="Month", ylab="Exchange Rate") + scale_x_discrete(breaks=c(1, 8, 16, 23), labels=c("Apr 2013", "Nov 2013", "Jul 2014", "Feb 2015"))
```

---

## Questions and Feedback?
<br />

If you have any questions, comments or feedback, please feel free to email me at zachf1989@gmail.com

Thank you for your time.